Supplementary Materials: Probing the Deuteron at Very Large Internal Momenta

### 2020-10-03 PRL_UTILITIES_CODES/prl_plot_tests/ms_wordcnt.tex
added prl_plot_tests directory where PRL word count is carefully monitored while is being updated. I also added additional plots to the supplemental material (rad./bc systematic plots)

simulation program, SIMC \cite{PhysRevC.64.054610}. Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization, 

@@

originated from the same reaction vertex at the target.\\

@@

over the kinematic bin. The systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found. The experimental and theoretical reduced cross sections were extracted and are defined as follows:

@@

>>>>

simulation program, SIMC \cite{PhysRevC.64.054610}(see Supplemental Material). Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization, 

@@

originated from the same reaction vertex at the target (See Supplemental Material). \\

@@

over the kinematic bin. The systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found (see Supplemental Material). The experimental and theoretical reduced cross sections were extracted and are defined as follows:

@@

%---include references that are not mentioned in the main text
%---but are included in the supplemental material
%---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
%\nocite{COSY}

### 2020-10-03 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
added prl_plot_tests directory where PRL word count is carefully monitored while is being updated. I also added additional plots to the supplemental material (rad./bc systematic plots)

\section{\large Systematic Uncertainty Studies on Event Selection Cuts}

@@

\includegraphics[scale=0.45]{plots/Em_syst.png}

@@

@@

kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:fig12} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in

@@

>>>>

\section{\large Systematic Uncertainty Studies on Event Selection Cuts, Radiative and Bin-Centering Corrections }

@@

\includegraphics[scale=0.4]{plots/Em_syst.png}

@@

\indent The systematic effect on the cross sections due to model dependency of the radiative and bin-centering corrections was investigated using the Barlow ratio approach described above.
In this case, the ratio was calculated from the difference between the experimental cross sections using the Laget PWIA and FSI models for both radiative and bin-centering corrections.
\includegraphics[scale=0.33]{plots/rad_sys.png}
\caption{Systematic effects of the radiative corrections model dependency on the data cross sections for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid) lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.  }
\includegraphics[scale=0.33]{plots/bc_sys.png}
\caption{Same as Fig. \ref{fig:fig12} but for bin-centering corrections.}
\label{fig:fig13}
Figures \ref{fig:fig12} and \ref{fig:fig13} show the Barlow ratio for radiative and bin-centering systematics is mostly within 2 standard deviations which show that
the model dependency on the correction factors have a negligible effect on the experimental cross sections.

@@

kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:fig14} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in

@@

\label{fig:fig14}
